---
title: "Introduction to m6ASeqTools"
author: "Hanna Lee"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to m6ASeqTools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(m6ASeqTools)
```

# Introduction
`m6ASeqTools` is an R package designed to streamline the post-processing and interpretation of site-level m6A predictions from m6Anet. It provides descriptive summaries of m6A distribution across transcripts, genes, biotypes, and transcript regions, and enables condition comparisons through a calculated weighted modification ratio. By integrating differential gene expression data, the package links methylation changes with expression differences, providing biotype-specific and region-specific insights into how m6A localization patterns relate to transcriptional regulation.

# Installation
`m6ASeqTools` can be installed on **Windows, macOS, and Linux**. It requires R (≥4.0).

```r
# Install devtools if needed
install.packages("devtools")

# Install Bioconductor dependencies
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install(c(
    "AnnotationDbi",
    "org.Hs.eg.db",
    "GenomicFeatures",
    "GenomicRanges",
    "IRanges",
    "S4Vectors"
))

# Install m6ASeqTools from GitHub
devtools::install_github("hannalee809/m6ASeqTools")
```


